%-----------PROJECTS-----------%
\section{Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading
    {\textbf{IMDB Clone} $|$ \emph{HTML5, CSS3, Javascript}}    {}
    \resumeItemListStart
        \resumeItem {Created a fully responsive web application for accessing movie information, increasing user accessibility by 40\% across several devices (e.g., smartphones, tablets, and PCs).}
        \resumeItem{Implemented an API integration to fetch and display movie details for over 10,000 movies, including titles, ratings, and synopses}
        \resumeItem{Designed a user-friendly feature to add movies to a favorites list, facilitating easy access to up to 20 favorite movies for personalized recommendations.}
        \resumeItem{brought a responsive approach that shows the most recent movie reviews along with succinct summaries, enhancing user decision-making by 40\% percent. .}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Habit Tracker App} $|$ \emph{React.js, SASS, Bootstrap, Redux}}{}
    \resumeItemListStart
        \resumeItem{Developed a habit tracking application using React.js, facilitating the creation and management of an unlimited number of habits.}
        \resumeItem{Using SASS and Bootstrap, an interactive weekly progress view was implemented to allow users to track their habit completion for the previous 7-days.}
          \resumeItem{Integrated a state management system (Redux) to provide a seamless user experience for marking habits as done, not done, or skipped.}
            \resumeItem{Designed a visually appealing interface using SASS, ensuring a user-friendly experience for managing an unlimited number of habits.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Placement-Cell}:$|$ \emph{NodeJs, ExpressJs, MongoDB, EJS, and JavaScript}}{}
    \resumeItemListStart
        \resumeItem{User or employee sign-up and sign-in}
        \resumeItem{Add and delete students.}
         \resumeItem{Allocate added student to the interview.}
         \resumeItem{Download the CSV report.}
    \resumeItemListEnd

\resumeSubHeadingListEnd